---
title: "Descriptive of PEF and ITW patients"
author: "AlfonsoDG"
date: "12/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### **Load of PEF and ITW kinetic data from Excel and descriptive of age data from patients with at least 2 kinetic cycles per limb**   
```{r echo=FALSE, warning=FALSE}

library(ggplot2)
library(readxl)
library(wesanderson)

DATOS_PEF_NIÑOS <- read_excel("/Volumes/ALFONSOONCE/ODIN_EXTRACTION/DATOS_PEF_NIÑOS.xlsx",
                              sheet = "PEF (NIÑOS)", range = "A1:E35")

DATOS_ITW <- read_excel("/Volumes/ALFONSOONCE/ODIN_EXTRACTION/DATOS_ITW.xlsx",
                        sheet = "ITW", range = "A1:E37")

datos_pef <- as.data.frame(DATOS_PEF_NIÑOS)

datos_pef <- datos_pef[which(datos_pef$EDAD <= 16),]
datos_pef <- datos_pef[which(datos_pef$`GRUPO (Nº ciclos)` == 2),]




datos_itw <- as.data.frame(DATOS_ITW)
datos_itw <- datos_itw[which(datos_itw$EDAD <= 16),]
datos_itw <- datos_itw[which(datos_itw$`GRUPO (Nº ciclos)` == 2),]



```

```{r}

## Summary of age from PEF
summary(datos_pef$EDAD)

## Summary of age from ITW
summary(datos_itw$EDAD)
  
```






### **Plot of PEF patients distributed by sex**  

```{r echo=FALSE}
count_M <- length(which(datos_pef$SEXO == "M"))
count_F <- length(which(datos_pef$SEXO == "F"))
v_M <- c("M", count_M)
v_F <- c("F", count_F)

data <- v_M
data <- as.data.frame(rbind(data, v_F))
data[] <- lapply(data, as.character)


e <- ggplot(data, aes(x = V1, y = as.integer(V2)))
e + geom_bar(aes(fill=V1), stat ="identity") +
  labs(x= "Sex", y="Count", title="PEF sex distribution", fill="Sex Group\n") +
  geom_text(aes(label=V2), vjust= -0.2, size=5) +
  ylim(0, max(as.integer(data$V2))*1.1) +
  theme_classic() +
  scale_fill_manual(values=wes_palette(n=3, name="GrandBudapest1")) +
  theme(plot.title = element_text(face= "bold", colour="black", size= 15, hjust = 0.5),
        axis.title.x = element_text(face="bold", colour="black", size = 12),
        axis.title.y = element_text(face="bold", colour="black", size = 12),
        legend.title = element_text(face="bold.italic", colour="black", size=10))
  

```


### **Plot of ITW patients distributed by sex**  

```{r echo=FALSE}
count_M <- length(which(datos_itw$SEXO == "M"))
count_F <- length(which(datos_itw$SEXO == "F"))
v_M <- c("M", count_M)
v_F <- c("F", count_F)

data2 <- v_M
data2 <- as.data.frame(rbind(data2, v_F))
data2[] <- lapply(data2, as.character)


e <- ggplot(data2, aes(x = V1, y = as.integer(V2)))
e + geom_bar(aes(fill=V1), stat ="identity") +
  labs(x= "Sex", y="Count", title="ITW sex distribution", fill="Sex Group\n") +
  geom_text(aes(label=V2), vjust= -0.2, size=5) +
  ylim(0, max(as.integer(data2$V2))*1.1) +
  theme_classic() +
  scale_fill_manual(values=wes_palette(n=3, name="GrandBudapest1")) +
  theme(plot.title = element_text(face= "bold", colour="black", size= 15, hjust = 0.5),
        axis.title.x = element_text(face="bold", colour="black", size = 12),
        axis.title.y = element_text(face="bold", colour="black", size = 12),
        legend.title = element_text(face="bold.italic", colour="black", size=10))
  

  
```


### **Distribution of PEF patients by age**  

```{r echo=FALSE}
age_pef <- datos_pef$EDAD
v_age <- seq(1:max(age_pef))
count <- vector(mode="integer", length=length(v_age))
for (i in min(v_age):max(v_age)){
  count[i] <- length(which(age_pef == i))
}

data_age_pef <- cbind(v_age, count)
ggplot(data.frame(data_age_pef),aes(x=as.factor(v_age), y=count)) +
  geom_bar(aes(fill=count), stat="identity") +
  scale_fill_gradient2(low="blue", high="red") +
  labs(x="Age", y="Count", title="PEF age distribution", fill ="No. of patients\n") +
  theme_classic() + 
  theme(plot.title = element_text(face= "bold", colour="black", size= 15, hjust = 0.5),
        axis.title.x = element_text(face="bold", colour="black", size = 12),
        axis.title.y = element_text(face="bold", colour="black", size = 12),
        legend.title = element_text(face="bold.italic", colour="black", size=10))
  
  
```


### **Distribution of ITW patients by age**  

```{r echo=FALSE}
age_itw <- datos_itw$EDAD
v_age <- seq(1:max(age_itw))
count <- vector(mode="integer", length=length(v_age))
for (i in min(v_age):max(v_age)){
  count[i] <- length(which(age_itw == i))
}

data_age_itw <- cbind(v_age, count)
ggplot(data.frame(data_age_itw),aes(x=as.factor(v_age), y=count)) +
  geom_bar(aes(fill=count), stat="identity") +
  scale_fill_gradient2(low="blue", high="red") +
  labs(x="Age", y="Count", title="ITW age distribution", fill="No. of patients\n") +
  theme_classic() + 
  theme(plot.title = element_text(face= "bold", colour="black", size= 15, hjust = 0.5),
        axis.title.x = element_text(face="bold", colour="black", size = 12),
        axis.title.y = element_text(face="bold", colour="black", size = 12),
        legend.title = element_text(face="bold.italic", colour="black", size=10))
  
  
```


### **Nº1 Age distribution of PEF patients by sex using a barchart**  

```{r echo=FALSE}
age_sex_pef <- datos_pef[,c(2,3)]
v_age_pef <- rep(seq(1:max(age_pef)),each=2)
count_age_pef <- vector(mode="integer", length=length(v_age_pef))
sex <- rep(c("M","F"), length.out=length(v_age_pef))
j=1

for (i in min(v_age_pef):max(v_age_pef)){
  count_age_pef[j] <- length(which(age_sex_pef$EDAD == i & age_sex_pef$SEXO == "M"))
  count_age_pef[j+1] <- length(which(age_sex_pef$EDAD == i & age_sex_pef$SEXO == "F"))
  j=j+2
}

e <- as.data.frame(cbind(v_age_pef, sex, count_age_pef))
e[] <- lapply(e, as.character)
x_axis_labels <- min(as.integer(e$v_age_pef)):max(as.integer(e$v_age_pef))

facet_plot <- ggplot(e, aes(x = as.numeric(v_age_pef), y = as.integer(count_age_pef))) +
  geom_bar(aes(fill=as.integer(count_age_pef)), stat = "identity", position = "dodge") +
  labs(x = "\n Age", y = "Count \n", title = "PEF age distribution by sex \n", fill= "No. of patients\n") +
  facet_grid(. ~ as.factor(e$sex)) +
  # scale_fill_gradient2(low="blue", high="red") +
  scale_fill_gradientn(colours = colorspace::diverge_hcl(7)) +
  theme_classic() +
  scale_x_continuous(labels = x_axis_labels, breaks = x_axis_labels) +
  theme(plot.title = element_text(face= "bold", colour="black", size= 15, hjust = 0.5), 
        axis.title.x = element_text(face="bold", colour="black", size = 12),
        axis.title.y = element_text(face="bold", colour="black", size = 12),
        legend.title = element_text(face="bold.italic", colour="black", size=10),
        strip.background = element_rect(fill="cyan", colour="black", size=1),
        strip.text = element_text(face="bold", size=rel(1.2)))

facet_plot  
  
```


### **Nº2 Age distribution of PEF patients by sex using a barchart**  

```{r echo=FALSE}
age_sex_pef <- datos_pef[,c(2,3)]
v_age_pef <- rep(seq(1:max(age_pef)),each=2)
count_age_pef <- vector(mode="integer", length=length(v_age_pef))
sex <- rep(c("M","F"), length.out=length(v_age_pef))
j=1

for (i in min(v_age_pef):max(v_age_pef)){
  count_age_pef[j] <- length(which(age_sex_pef$EDAD == i & age_sex_pef$SEXO == "M"))
  count_age_pef[j+1] <- length(which(age_sex_pef$EDAD == i & age_sex_pef$SEXO == "F"))
  j=j+2
}

e <- as.data.frame(cbind(v_age_pef, sex, count_age_pef))
e[] <- lapply(e, as.character)
x_axis_labels <- min(as.integer(e$v_age_pef)):max(as.integer(e$v_age_pef))

plot_2 <- ggplot(e, aes(fill=sex, y=as.integer(count_age_pef), x=as.integer(v_age_pef))) + 
  geom_bar(aes(fill=sex), position="dodge", stat="identity") +
  labs(x= "\n Age", y= "Count \n", title ="PEF age distribution by gender \n", fill= "Sex Group\n") +
  # scale_fill_gradientn(colours = colorspace::diverge_hcl(7)) +
  scale_fill_manual(values=wes_palette(n=3, name="GrandBudapest1")) +
  theme_classic() +
  scale_x_continuous(labels = x_axis_labels, breaks = x_axis_labels) +
  theme(plot.title = element_text(face= "bold", colour="black", size= 15, hjust = 0.5), 
        axis.title.x = element_text(face="bold", colour="black", size = 12),
        axis.title.y = element_text(face="bold", colour="black", size = 12),
        legend.title = element_text(face="bold.italic", colour="black", size=10))
  
plot_2
  
```



### **Nº1 Age distribution of ITW patients by sex using a barchart**  

```{r echo=FALSE}
age_sex_itw <- datos_itw[,c(2,3)]
v_age_itw <- rep(seq(1:max(age_itw)),each=2)
count_age_itw <- vector(mode="integer", length=length(v_age_itw))
sex <- rep(c("M","F"), length.out=length(v_age_itw))
j=1

for (i in min(v_age_itw):max(v_age_itw)){
  count_age_itw[j] <- length(which(age_sex_itw$EDAD == i & age_sex_itw$SEXO == "M"))
  count_age_itw[j+1] <- length(which(age_sex_itw$EDAD == i & age_sex_itw$SEXO == "F"))
  j=j+2
}

e <- as.data.frame(cbind(v_age_itw, sex, count_age_itw))
e[] <- lapply(e, as.character)
x_axis_labels <- min(as.integer(e$v_age_itw)):max(as.integer(e$v_age_itw))

facet_plot <- ggplot(e, aes(x = as.numeric(v_age_itw), y = as.integer(count_age_itw))) +
  geom_bar(aes(fill=as.integer(count_age_itw)), stat = "identity", position = "dodge") +
  labs(x = "\n Age", y = "Count \n", title = "ITW age distribution by sex \n", fill= "No. of patients\n") +
  facet_grid(. ~ as.factor(e$sex)) +
  scale_fill_gradientn(colours = colorspace::diverge_hcl(7)) +
  # scale_fill_manual(breaks=c("4","3","2","1","0"), values=wes_palette(n=5, name="Zissou1")) +
  theme_classic() +
  scale_x_continuous(labels = x_axis_labels, breaks = x_axis_labels) +
  theme(plot.title = element_text(face= "bold", colour="black", size= 15, hjust = 0.5), 
        axis.title.x = element_text(face="bold", colour="black", size = 12),
        axis.title.y = element_text(face="bold", colour="black", size = 12),
        legend.title = element_text(face="bold.italic", colour="black", size=10),
        strip.background = element_rect(fill="cyan", colour="black", size=1),
        strip.text = element_text(face="bold", size=rel(1.2)))

facet_plot  
  
```




### **Nº2 Age distribution of PEF patients by sex using a barchart**  

```{r echo=FALSE}
age_sex_itw <- datos_itw[,c(2,3)]
v_age_itw <- rep(seq(1:max(age_itw)),each=2)
count_age_itw <- vector(mode="integer", length=length(v_age_itw))
sex <- rep(c("M","F"), length.out=length(v_age_itw))
j=1

for (i in min(v_age_itw):max(v_age_itw)){
  count_age_itw[j] <- length(which(age_sex_itw$EDAD == i & age_sex_itw$SEXO == "M"))
  count_age_itw[j+1] <- length(which(age_sex_itw$EDAD == i & age_sex_itw$SEXO == "F"))
  j=j+2
}

e <- as.data.frame(cbind(v_age_itw, sex, count_age_itw))
e[] <- lapply(e, as.character)
x_axis_labels <- min(as.integer(e$v_age_itw)):max(as.integer(e$v_age_itw))

plot_2 <- ggplot(e, aes(fill=sex, y=as.integer(count_age_itw), x=as.integer(v_age_itw))) + 
  geom_bar(aes(fill=sex), position="dodge", stat="identity") +
  labs(x= "\n Age", y= "Count \n", title ="ITW age distribution by gender \n", fill= "Sex Group\n") +
  # scale_fill_gradientn(colours = colorspace::diverge_hcl(7)) +
  scale_fill_manual(values=wes_palette(n=3, name="GrandBudapest1")) +
  theme_classic() +
  scale_x_continuous(labels = x_axis_labels, breaks = x_axis_labels) +
  theme(plot.title = element_text(face= "bold", colour="black", size= 15, hjust = 0.5), 
        axis.title.x = element_text(face="bold", colour="black", size = 12),
        axis.title.y = element_text(face="bold", colour="black", size = 12),
        legend.title = element_text(face="bold.italic", colour="black", size=10))
  
plot_2
  
```
